---
title: "Fragment Comparison VSLSADPEQEVR"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
require(knitr)
opts_knit$set(root.dir = "G:/Projects/Proteomics/Zymomona")
knitr::opts_chunk$set(root.dir = "G:/Projects/Proteomics/Zymomona/DataAnalysis/", warning = FALSE, message = FALSE)
```

```{r install_packages, echo=FALSE}
library(pcaMethods)
library(ggplot2)
library(pheatmap)
library(plotly)
library(reshape2)
library(RColorBrewer)
library(plyr)
```

```{r load_data, echo=FALSE}
# These are dataframes for infusions samples monitoring the summed intensity for 10 b and y fragment in the peptide VSLSADPEQEVR 
CompiledFragments_0_4_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_4_Zymo_noFAIMS.csv", 
                                            header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_0_4_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_4_Zymo_FAIMS.csv", 
                                          header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_0_6_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_6_Zymo_noFAIMS.csv", 
                                          header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_0_6_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_6_Zymo_FAIMS.csv", 
                                        header = TRUE, sep = ",", stringsAsFactors = FALSE)

CompiledFragments_0_8_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_8_Zymo_noFAIMS.csv", 
                                          header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_0_8_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_0_8_Zymo_FAIMS.csv", 
                                        header = TRUE, sep = ",", stringsAsFactors = FALSE)
X20200126_ZymoFAIMS_IW_0_8_R120K_MI1_AGC1e06_3.raw <- rep(0,nrow(CompiledFragments_0_8_FAIMS))
CompiledFragments_0_8_FAIMS <- cbind(CompiledFragments_0_8_FAIMS[,1:4],X20200126_ZymoFAIMS_IW_0_8_R120K_MI1_AGC1e06_3.raw,CompiledFragments_0_8_FAIMS[,5:ncol(CompiledFragments_0_8_FAIMS)])

CompiledFragments_1_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_1_Zymo_noFAIMS.csv", 
                                          header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_1_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_1_Zymo_FAIMS.csv", 
                                        header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_1_3_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_1_3_Zymo_noFAIMS.csv", 
                                        header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_1_3_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_1_3_Zymo_FAIMS.csv", 
                                      header = TRUE, sep = ",", stringsAsFactors = FALSE)

CompiledFragments_2_noFAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_2_Zymo_noFAIMS.csv", 
                                          header = TRUE, sep = ",", stringsAsFactors = FALSE)


CompiledFragments_2_FAIMS <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/SummedIntensity_Infusions/VSLSADPEQEVR/CompiledFragmentResults_IW_2_Zymo_FAIMS.csv", 
                                        header = TRUE, sep = ",", stringsAsFactors = FALSE)


```

```{r dataformatting, echo=FALSE}
# x = CompiledFragments_0_8_FAIMS
meta_replicates <- function(x){
  samples <- colnames(x[,-c(1:2)])
  samples <- gsub("^.*?_R","R",samples)
  
  df <- x[,-c(1:2)]
  rownames(df) <- x$Mass.Feature
  colnames(df) <- samples
  df[df == 0] <- NA
  
  df <- df[-which(rownames(df)=="b1"),]
  df <- df[-which(rownames(df)=="y1"),]
  
  df_t <- t(df)
  
  meta <- as.data.frame(stringr::str_split_fixed(rownames(df_t),"_",4))
  colnames(meta) <- c("Resolution", "MaxInjection", "AGC", "Replicate")
  
  meta[,1] <- sub('R','', meta[,1])
  
  meta[,2] <- sub('MI', '', meta[,2])
  meta[,2] <- sub(502, 0.502, meta[,2])
  meta[,2] <- as.factor(as.numeric(meta[,2]))
  
  meta[,4] <- as.numeric(sub("*.raw",'', meta[,4]))
  
  rownames(meta) <- rownames(df_t)
  meta <- meta[order(meta[,1],meta[,2]),]
  
  return(meta)
  
}


# x = CompiledFragments_0_4_FAIMS
# m = meta_0_4_noFAIMS
# m = meta
df_fragments_log2 <- function(x,m){
  samples <- colnames(x[,-c(1:2)])
  samples <- gsub("^.*?_R","R",samples)
  
  df <- x[,-c(1:2)]
  rownames(df) <- x$Mass.Feature
  colnames(df) <- samples
  df[df == 0] <- NA
  
  df_log2 <- log2(df)
  df_log2[is.na(df_log2)] <- 0
  
  df_log2 <- df_log2[-which(rownames(df_log2)=="b1"),]
  df_log2 <- df_log2[-which(rownames(df_log2)=="y1"),]
  
  for(i in 1:ncol(df_log2)){
    mostIntense = max(df_log2[,i])
    
    for(j in 1:nrow(df_log2)){
      df_log2[j,i] <- df_log2[j,i]/mostIntense
    }
  }

  df_log2 <- df_log2[rownames(m)]
  
  return(df_log2)
  
}
```

```{r df_log2_meta ,echo=FALSE}

meta_0_4_noFAIMS <- meta_replicates(CompiledFragments_0_4_noFAIMS)
df_0_4_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_0_4_noFAIMS,meta_0_4_noFAIMS)

meta_0_4_FAIMS <- meta_replicates(CompiledFragments_0_4_FAIMS)
df_0_4_FAIMS_log2 <- df_fragments_log2(CompiledFragments_0_4_FAIMS, meta_0_4_FAIMS)


meta_0_6_noFAIMS <- meta_replicates(CompiledFragments_0_6_noFAIMS)
df_0_6_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_0_6_noFAIMS, meta_0_6_noFAIMS)

meta_0_6_FAIMS <- meta_replicates(CompiledFragments_0_6_FAIMS)
df_0_6_FAIMS_log2 <- df_fragments_log2(CompiledFragments_0_6_FAIMS, meta_0_6_FAIMS)


meta_0_8_noFAIMS <- meta_replicates(CompiledFragments_0_8_noFAIMS)
df_0_8_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_0_8_noFAIMS, meta_0_8_noFAIMS)

meta_0_8_FAIMS <- meta_replicates(CompiledFragments_0_8_FAIMS)
df_0_8_FAIMS_log2 <- df_fragments_log2(CompiledFragments_0_8_FAIMS, meta_0_8_FAIMS)


meta_1_noFAIMS <- meta_replicates(CompiledFragments_1_noFAIMS)
df_1_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_1_noFAIMS,meta_1_noFAIMS)

meta_1_FAIMS <- meta_replicates(CompiledFragments_1_FAIMS)
df_1_FAIMS_log2 <- df_fragments_log2(CompiledFragments_1_FAIMS, meta_1_FAIMS)


meta_1_3_noFAIMS <- meta_replicates(CompiledFragments_1_3_noFAIMS)
df_1_3_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_1_3_noFAIMS, meta_1_3_noFAIMS)

meta_1_3_FAIMS <- meta_replicates(CompiledFragments_1_3_FAIMS)
df_1_3_FAIMS_log2 <- df_fragments_log2(CompiledFragments_1_3_FAIMS, meta_1_3_FAIMS)


meta_2_noFAIMS <- meta_replicates(CompiledFragments_2_noFAIMS)
df_2_noFAIMS_log2 <- df_fragments_log2(CompiledFragments_2_noFAIMS, meta_2_noFAIMS)

meta_2_FAIMS <- meta_replicates(CompiledFragments_2_FAIMS)
df_2_FAIMS_log2 <- df_fragments_log2(CompiledFragments_2_FAIMS, meta_2_FAIMS)
```



```{r Annotations, echo=FALSE}
#x = df_0_4_noFAIMS_log2
#m = meta_0_4_noFAIMS
replicate_annotation <- function(x,m){
  annotation_res = data.frame(Resolution = m$Resolution)
  rownames(annotation_res) <- colnames(x)
  
  annotation_MI = data.frame(MaxInjection = m$MaxInjection)
  rownames(annotation_MI) <- colnames(x)
  
  annotation = cbind(annotation_res, annotation_MI)
  
  return(annotation)
}

annotation_0_4_noFAIMS <- replicate_annotation(df_0_4_noFAIMS_log2, meta_0_4_noFAIMS)
annotation_0_6_noFAIMS <- replicate_annotation(df_0_6_noFAIMS_log2, meta_0_6_noFAIMS)
annotation_0_8_noFAIMS <- replicate_annotation(df_0_4_noFAIMS_log2, meta_0_8_noFAIMS)
annotation_1_noFAIMS <- replicate_annotation(df_1_noFAIMS_log2, meta_1_noFAIMS)
annotation_1_3_noFAIMS <- replicate_annotation(df_1_3_noFAIMS_log2, meta_1_3_noFAIMS)
annotation_2_noFAIMS <- replicate_annotation(df_2_noFAIMS_log2, meta_2_noFAIMS)

annotation_0_4_FAIMS <- replicate_annotation(df_0_4_FAIMS_log2, meta_0_4_FAIMS)
annotation_0_6_FAIMS <- replicate_annotation(df_0_6_FAIMS_log2, meta_0_6_FAIMS)
annotation_0_8_FAIMS <- replicate_annotation(df_0_8_FAIMS_log2, meta_0_8_FAIMS)
annotation_1_FAIMS <- replicate_annotation(df_1_FAIMS_log2, meta_1_FAIMS)
annotation_1_3_FAIMS <- replicate_annotation(df_1_3_FAIMS_log2, meta_1_3_FAIMS)
annotation_2_FAIMS <- replicate_annotation(df_2_FAIMS_log2, meta_2_FAIMS)
```



```{r,echo=FALSE}

#noFAIMS.list <- list(df_0_4_noFAIMS,df_0_6_noFAIMS_log2,df_0_8_noFAIMS_log2,df_1_noFAIMS_log2, df_1_3_noFAIMS_log2, df_2_noFAIMS_log2)
#FAIMS.list <- list(df_0_4_FAIMS_log2,df_0_6_FAIMS_log2,df_0_8_FAIMS_log2, df_1_FAIMS_log2, df_1_3_FAIMS_log2, df_2_FAIMS_log2)


my_colour = list(
  #MaxInjection = c(`0.502` = "#CEE3DD", `1` = "#A7C2A4", `5` = "#73A08A"),
  MaxInjection = c(`0.502` = "#F7F7F7", `1` = "#D0D3CA", `5` = "#A3A79D"),
  Resolution = c(`120K` = "#FFEC77", `240K` = "#FFBE5E", `500K` = "#DB664F")
  #Resolution = c(`120K` = "#E2C044", `240K` = "#DB7C26", `500K` = "#DB5A42")
)

cols <- brewer.pal(3, "YlGnBu")
scaleRYG <- colorRampPalette(cols)(20)
#scaleRYG <- colorRampPalette(c("#F5F5F5","#E6F598","#78A073"))(20)


pheatmap(df_0_4_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_4_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.4 Da - Parameter Comparisons Infusions")

pheatmap(df_0_4_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_4_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.4 Da with FAIMS") 

pheatmap(df_0_6_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_6_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.6 Da - Parameter Comparisons Infusions")

pheatmap(df_0_6_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_6_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.6 Da with FAIMS") 


pheatmap(df_0_8_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_8_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.8 Da - Parameter Comparisons Infusions")

pheatmap(df_0_8_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_0_8_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         #gaps_col =c(8,17,26),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.8 Da with FAIMS") 


pheatmap(df_1_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_1_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1 Da - Parameter Comparisons Infusions")

pheatmap(df_1_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_1_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1 Da with FAIMS") 

pheatmap(df_1_3_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_1_3_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1.3 Da - Parameter Comparisons Infusions")

pheatmap(df_1_3_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_1_3_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,17,26),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1.3 Da with FAIMS") 

pheatmap(df_2_noFAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_2_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(10,19,28),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 2 Da - Parameter Comparisons Infusions")

pheatmap(df_2_FAIMS_log2,
         #annotation = annotation_res,
         annotation_colors = my_colour,
         annotation_col = annotation_2_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 2 Da with FAIMS") 
```

```{r averagedIntensities, echo=FALSE}

Experiment_meta <- data.frame(IsolationWidth = c("0_4","0_6","0_8","1","1_3","2")) 
IW_sample_noFAIMS = vector()
  for(i in 1:length(Experiment_meta$IsolationWidth)){
    IW_sample_noFAIMS = append(IW_sample_noFAIMS, paste0("df_",Experiment_meta$IsolationWidth[i],"_noFAIMS_log2"))
  }
IW_sample_FAIMS = vector()
for(i in 1:length(Experiment_meta$IsolationWidth)){
  IW_sample_FAIMS = append(IW_sample_FAIMS, paste0("df_",Experiment_meta$IsolationWidth[i],"_FAIMS_log2"))
}
Experiment_meta$FAIMS <- IW_sample_FAIMS

#x <- CompiledFragments_2_noFAIMS
#x=CompiledFragments_0_8_FAIMS
averagedIntensity <- function(x){
  
  samples <- colnames(x[,-c(1:2)])
  samples <- gsub("^.*?_R","R",samples)
  samples <- gsub("_AGC.*","", samples)
  
  df_t <- as.data.frame(t(x[,-c(1,2)]))
  colnames(df_t) <- x$Mass.Feature
  
  df_t[df_t == 0] <- NA
  
  df_t <- df_t[,-which(colnames(df_t)=="b1")]
  df_t <- df_t[,-which(colnames(df_t)=="y1")]
  
  df_t <- as.data.frame(cbind(samples, df_t))
  
  if(length(grep("CORRUPTED",rownames(df_t))) != 0){
    df_t <- df_t[-grep("CORRUPTED",rownames(df_t)),]
  }
  
  for(i in 1:26){
    #print(i)
    #print(rowSums(is.na(df_t[i,])) == length(df_t[i,-1]))
    if(rowSums(is.na(df_t[i,])) == length(df_t[i,-1])){
      df_t <- df_t[-c(i),]
    }
  }
  
  df_t_averaged <- aggregate(df_t[,-1], by = list(df_t$samples), mean)
  #rownames(df_t_averaged) <- df_t_averaged$Group.1
  
  
  meta_unique <- as.data.frame(stringr::str_split_fixed(df_t_averaged$Group.1,"_",2))
  colnames(meta_unique) <- c("Resolution", "MaxInjection")
  
  meta_unique[,1] <- sub('R','', meta_unique[,1])
  
  meta_unique[,2] <- sub('MI', '', meta_unique[,2])
  meta_unique[,2] <- sub(502, 0.502, meta_unique[,2])
  meta_unique[,2] <- as.factor(as.numeric(meta_unique[,2]))
  
  meta_unique <- meta_unique[order(meta_unique[,1],meta_unique[,2]),]
  
  #rownames(df_t_averaged) <- as.character(seq(from = 1, to = length(rownames(df_t_averaged)), by =1))
  df_t_averaged_ordered <- log2(df_t_averaged[rownames(meta_unique),-1])
  #rownames(df_t_averaged) <- 
  rownames(df_t_averaged_ordered) <- df_t_averaged$Group.1[as.numeric(rownames(df_t_averaged_ordered))]
  
  df_t_averaged_ordered[is.na(df_t_averaged_ordered)] <- 0
  df_averaged_ordered <- t(df_t_averaged_ordered)
  
      for(i in 1:ncol(df_averaged_ordered)){
        
        mostIntense = max(df_averaged_ordered[,i])
        
        if(mostIntense == 0){
          
        }else{
            for(j in 1:nrow(df_averaged_ordered)){
            df_averaged_ordered[j,i] <- df_averaged_ordered[j,i]/mostIntense
          }
        }
        

    }
  
  return(df_averaged_ordered)

}

#x = annotation_0_4_FAIMS
unique_annotation <- function(x){
  x$sample.names <- sub('_AGC.*', '',rownames(x))
  x <- x[!duplicated(x$sample.names),]
  rownames(x) <- x$sample.names
  
  return(x[,-3])
}
```

```{r,echo=FALSE}
unique_annotation_0_4_noFAIMS <- unique_annotation(annotation_0_4_noFAIMS)
averaged_0_4_noFAIMS_log2 <- averagedIntensity(CompiledFragments_0_4_noFAIMS)

unique_annotation_0_4_FAIMS <- unique_annotation(annotation_0_4_FAIMS)
averaged_0_4_FAIMS_log2 <- averagedIntensity(CompiledFragments_0_4_FAIMS)

unique_annotation_0_6_noFAIMS <- unique_annotation(annotation_0_6_noFAIMS)
averaged_0_6_noFAIMS_log2 <- averagedIntensity(CompiledFragments_0_6_noFAIMS)

unique_annotation_0_6_FAIMS <- unique_annotation(annotation_0_6_FAIMS)
averaged_0_6_FAIMS_log2 <- averagedIntensity(CompiledFragments_0_6_FAIMS)

unique_annotation_0_8_noFAIMS <- unique_annotation(annotation_0_8_noFAIMS)
averaged_0_8_noFAIMS_log2 <- averagedIntensity(CompiledFragments_0_8_noFAIMS)

unique_annotation_0_8_FAIMS <- unique_annotation(annotation_0_8_FAIMS)
averaged_0_8_FAIMS_log2 <- averagedIntensity(CompiledFragments_0_8_FAIMS)

unique_annotation_1_noFAIMS <- unique_annotation(annotation_1_noFAIMS)
averaged_1_noFAIMS_log2 <- averagedIntensity(CompiledFragments_1_noFAIMS)

unique_annotation_1_FAIMS <- unique_annotation(annotation_1_FAIMS)
averaged_1_FAIMS_log2 <- averagedIntensity(CompiledFragments_1_FAIMS)

unique_annotation_1_3_noFAIMS <- unique_annotation(annotation_1_3_noFAIMS)
averaged_1_3_noFAIMS_log2 <- averagedIntensity(CompiledFragments_1_3_noFAIMS)

unique_annotation_1_3_FAIMS <- unique_annotation(annotation_1_3_FAIMS)
averaged_1_3_FAIMS_log2 <- averagedIntensity(CompiledFragments_1_3_FAIMS)

unique_annotation_2_noFAIMS <- unique_annotation(annotation_2_noFAIMS)
averaged_2_noFAIMS_log2 <- averagedIntensity(CompiledFragments_2_noFAIMS)

unique_annotation_2_FAIMS <- unique_annotation(annotation_2_FAIMS)
averaged_2_FAIMS_log2 <- averagedIntensity(CompiledFragments_2_FAIMS)

```

```{r}
my_colour = list(
  #MaxInjection = c(`0.502` = "#CEE3DD", `1` = "#A7C2A4", `5` = "#73A08A"),
  MaxInjection = c(`0.502` = "#F7F7F7", `1` = "#D0D3CA", `5` = "#A3A79D"),
  Resolution = c(`120K` = "#FFEC77", `240K` = "#FFBE5E", `500K` = "#DB664F")
  #Resolution = c(`120K` = "#E2C044", `240K` = "#DB7C26", `500K` = "#DB5A42")
)

cols <- brewer.pal(3, "YlGnBu")
scaleRYG <- colorRampPalette(cols)(20)
#scaleRYG <- colorRampPalette(c("#F5F5F5","#E6F598","#78A073"))(20)

pheatmap(averaged_0_4_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_4_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.4 Da")

pheatmap(averaged_0_4_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_4_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.4 Da with FAIMS")

pheatmap(averaged_0_6_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_6_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.6 Da")

pheatmap(averaged_0_6_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_6_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.6 Da with FAIMS")

pheatmap(averaged_0_8_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_8_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.8 Da")

pheatmap(averaged_0_8_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_8_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 0.8 Da with FAIMS")

pheatmap(averaged_1_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1 Da")

pheatmap(averaged_1_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1 Da with FAIMS")

pheatmap(averaged_1_3_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_3_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1.3 Da")

pheatmap(averaged_1_3_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_3_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 1.3 Da with FAIMS")

pheatmap(averaged_2_noFAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_2_noFAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 2 Da")

pheatmap(averaged_2_FAIMS_log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_2_FAIMS,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1),
         show_colnames = F,
         main = "IW of 2 Da with FAIMS")

```

```{r}
# To combine noFaims and FAIMs samples into one heatmap
#x1 <- CompiledFragments_2_noFAIMS
#x2 <- CompiledFragments_2_FAIMS
# x = CompiledFragments_2_noFAIMS
format_df <- function(x){
  samples <- colnames(x[,-c(1:2)])
  samples <- gsub("^.*?_R","R",samples)
  
  df <- x[,-c(1:2)]
  rownames(df) <- x$Mass.Feature
  colnames(df) <- samples
  df[df == 0] <- NA
  
  df_log2 <- log2(df)
  df_log2[is.na(df_log2)] <- 0
  
  df_log2 <- df_log2[-which(rownames(df_log2)=="b1"),]
  df_log2 <- df_log2[-which(rownames(df_log2)=="y1"),]
  
    if(length(grep("CORRUPTED",colnames(df_log2))) != 0){
    df_log2 <- df_log2[,-grep("CORRUPTED",colnames(df_log2))]
  }
  
  return(df_log2)

}



combined_replicates_Log2 <- function(x1,x2){
  
  df_noFAIMS_log2 <- format_df(x1)
  df_FAIMS_log2 <- format_df(x2)
  
  fragments <- rownames(df_FAIMS_log2)
  
  fragment_FAIMS = vector()
  for(i in fragments){fragment_FAIMS = append(fragment_FAIMS,paste0(i,'_FAIMS', collapse = " "))}
  rownames(df_FAIMS_log2) <- fragment_FAIMS
  
  
  
  Combined_Log2 <- rbind(df_noFAIMS_log2, df_FAIMS_log2)
  
        for(i in 1:ncol(Combined_Log2)){
        
        mostIntense = max(Combined_Log2[,i])
        
        if(mostIntense == 0){
          
        }else{
            for(j in 1:nrow(Combined_Log2)){
            Combined_Log2[j,i] <- Combined_Log2[j,i]/mostIntense
          }
        }

        }
  return(Combined_Log2)
  
}

# x <- Combined_0_4_rep_Log2
combined_Log2 <- function (x){
  samples <- colnames(x)
  samples <- sub('_AGC.*', '', samples)
  
  t_x <- as.data.frame(t(x)) #need to create a dataframe before cbind with a vector that will be factorized
  t_x <- cbind(samples, t_x)
  
  
  rownames(t_x)
  
  t_x_averaged <- aggregate(t_x[,-1], by = list(t_x$samples), mean)
  
  meta_unique <- as.data.frame(stringr::str_split_fixed(t_x_averaged$Group.1,"_",2))
  colnames(meta_unique) <- c("Resolution", "MaxInjection")
  
  meta_unique[,1] <- sub('R','', meta_unique[,1])
  
  meta_unique[,2] <- sub('MI', '', meta_unique[,2])
  meta_unique[,2] <- sub(502, 0.502, meta_unique[,2])
  meta_unique[,2] <- as.factor(as.numeric(meta_unique[,2]))
  
  meta_unique <- meta_unique[order(meta_unique[,1],meta_unique[,2]),]
  
  #rownames(df_t_averaged) <- as.character(seq(from = 1, to = length(rownames(df_t_averaged)), by =1))
  t_x_averaged_ordered <- t_x_averaged[rownames(meta_unique),-1]
  #rownames(df_t_averaged) <- 
  rownames(t_x_averaged_ordered) <- t_x_averaged$Group.1[as.numeric(rownames(t_x_averaged_ordered))]
  
  x_averaged_ordered <- as.data.frame(t(t_x_averaged_ordered))
  
  return(x_averaged_ordered)

}
```

```{r,echo=FALSE}


my_colour = list(
  #MaxInjection = c(`0.502` = "#CEE3DD", `1` = "#A7C2A4", `5` = "#73A08A"),
  MaxInjection = c(`0.502` = "#F7F7F7", `1` = "#D0D3CA", `5` = "#A3A79D"),
  Resolution = c(`120K` = "#FFEC77", `240K` = "#FFBE5E", `500K` = "#DB664F"),
  IonMobility = c(`FAIMS`= "#F9E7E7", `no FAIMS` = "#EDF7F6")
  #Resolution = c(`120K` = "#E2C044", `240K` = "#DB7C26", `500K` = "#DB5A42")
)

Combined_0_4_rep_Log2 <- combined_replicates_Log2(CompiledFragments_0_4_noFAIMS,CompiledFragments_0_4_FAIMS)
Combined_0_6_rep_Log2 <- combined_replicates_Log2(CompiledFragments_0_6_noFAIMS,CompiledFragments_0_6_FAIMS)
Combined_0_8_rep_Log2 <- combined_replicates_Log2(CompiledFragments_0_8_noFAIMS,CompiledFragments_0_8_FAIMS)
Combined_1_rep_Log2 <- combined_replicates_Log2(CompiledFragments_1_noFAIMS,CompiledFragments_1_FAIMS)
Combined_1_3_rep_Log2 <- combined_replicates_Log2(CompiledFragments_1_3_noFAIMS,CompiledFragments_1_3_FAIMS)
Combined_2_rep_Log2 <- combined_replicates_Log2(CompiledFragments_2_noFAIMS,CompiledFragments_2_FAIMS)

pheatmap(Combined_0_4_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_0_4_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.4 Da")

pheatmap(Combined_0_6_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_0_6_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.6 Da")

pheatmap(Combined_0_8_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_0_8_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.8 Da")

pheatmap(Combined_1_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_1_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 1 Da")

pheatmap(Combined_1_3_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_1_3_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 1.3 Da")

pheatmap(Combined_2_rep_Log2,
         annotation_colors = my_colour,
         annotation_col = annotation_2_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(9,18,27),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 2 Da")


```


```{r,echo=FALSE}
Combined_0_4_Log2 <- combined_Log2(Combined_0_4_rep_Log2)
Combined_0_6_Log2 <- combined_Log2(Combined_0_6_rep_Log2)
Combined_0_8_Log2 <- combined_Log2(Combined_0_8_rep_Log2)
Combined_1_Log2 <- combined_Log2(Combined_1_rep_Log2)
Combined_1_3_Log2 <- combined_Log2(Combined_1_3_rep_Log2)
Combined_2_Log2 <- combined_Log2(Combined_2_rep_Log2)

pheatmap(Combined_0_4_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_4_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.4 Da")

pheatmap(Combined_0_6_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_6_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.6 Da")

pheatmap(Combined_0_8_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_0_8_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 0.8 Da")

pheatmap(Combined_1_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 1 Da")

pheatmap(Combined_1_3_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_1_3_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 1.3 Da")

pheatmap(Combined_2_Log2,
         annotation_colors = my_colour,
         annotation_col = unique_annotation_2_noFAIMS,
         #annotation_row = fragment_annotation,
         color = scaleRYG,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         gaps_col =c(3,6,9),
         gaps_row = c(1,19,20),
         show_colnames = F,
         main = "IW of 2 Da")


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
