---
title: "ISPH proteins and peptides"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
require(knitr)
opts_knit$set(root.dir = "I:/EAT_BackUP/Trujillo_34362342_44636349_SN_Data/P2/Complete/Projects/Proteomics/Zymomona")
knitr::opts_chunk$set(root.dir = "I:/EAT_BackUP/Trujillo_34362342_44636349_SN_Data/P2/Complete/Projects/Proteomics/Zymomona/DataAnalysis/", warning = FALSE, message = FALSE)
```

```{r install_packages, echo=FALSE}
library(pcaMethods)
library(ggplot2)
library(plotly)
library(reshape2)
library(plyr)

```

```{r load_data, echo=FALSE}
# Read in MaxQuant output proteingroups, peptides as well as DRB imputed dataframe in Data_Formatting_Functions
load("P:/EAT_20190926_Zymomona/ISPH_ISPG_OE_Mehmet/EclipseRuns/combined_ZM4tag/txt/OEZM4tag_45minLCMSMS_Eclipse_AbundanceImputed_20200420.RData")
```

I reformatted both the protein and peptide MaxQuant .csv files to extract ISPH data and the three associated peptides **AIEIVDQALDR**, **GLPVVDATCPLVNK**, and **FTDVIGPDTSDICYATQNR**

I built the following functions that utilized certain data to output formatted data frames.  
1. *ISPH_reformat_ZM4* function takes in gene = ZMO0875, the filtered and imputed protein intensities, and the peptide intensities. The output is ISPH abundance table in wide format that contains abundances for the peptides of interest.  
2. *peptide_FC* function takes in the column number associated with the peptide of interest and ISPH abundance table. This function will produce the fold changes of the proteins and peptides relative to what was measured in the WT.  


```{r ISPH_data_formating, echo=FALSE}
#df <- merged_drb_impute
#df_peptide <- ISPH_peptides
#gene = "ZMO0875"
ISPH_reformat_ZM4 <- function(gene,df, peptide,df_peptide){
  #Extract "ZMO0875" row
  ISPH_data <- df[grep(gene, df$Protein.IDs),]
  #Reduce dataframe to only LFQ columns
  ISPH_lfq <- ISPH_data[, c(1,grep("LFQ", colnames(ISPH_data)))]
  #For loop to save the each peptide intensity into a vector
  for(i in 1:length(peptide)){
    ISPH_peptide_lfq <- df_peptide[which(df_peptide$Sequence == peptide[i]),grep("Intensity", colnames(df_peptide))] 
    ISPH_peptide_lfq <- ISPH_peptide_lfq[,-grep("new", colnames(ISPH_peptide_lfq))]
    assign(paste(peptide[i],"_lfq",sep = ""), vapply(ISPH_peptide_lfq[1,-1], paste, collapse = ",", character(1L)))
  }
  
  # save sample names in a vector
  Sample <- sub("LFQ.intensity.", "", colnames(ISPH_lfq[,-1]))
  # Save intenisty of ISPH protein in a vector
  Intensity <- unlist(ISPH_lfq[2:ncol(ISPH_lfq)])
  ISPH_lfq <- data.frame("Sample" = Sample, "Intensity" = Intensity)
  ISPH_lfq$AIEIVDQALDR <- as.numeric(AIEIVDQALDR_lfq)
  ISPH_lfq$GLPVVDATCPLVNK <- as.numeric(GLPVVDATCPLVNK_lfq)
  ISPH_lfq$FTDVIGPDTSDICYATQNR <- as.numeric(FTDVIGPDTSDICYATQNR_lfq)
  ISPH_lfq$Type <- c("ISPG","ISPG","ISPG","ISPH","ISPH","ISPH","WT","WT","WT")
  
  v = vector()
  WT_lfq <- ISPH_lfq[grep("WT",rownames(ISPH_lfq)),2]
  
    for (j in 1:nrow(ISPH_lfq)) {
      for (i in 1:3) {
      if(length(grep(i,ISPH_lfq$Sample[j])) != 0){
        v <- append(v,ISPH_lfq$Intensity[j]/WT_lfq[i])
        #print(v)
        }
      }
    }
  ISPH_lfq$FC <- v
  return(ISPH_lfq)
}
# df <- ISPH_lfq
# colnum will be 3,4,5
peptide_FC <- function(colnum,df){
  v = numeric(0)
  WT_lfq <- as.numeric(df[grep("WT",rownames(df)),colnum])
  
  for (j in 1:nrow(df)) {
    for (i in 1:3) {
      if(length(grep(i,df$Sample[j])) != 0){
        v <- append(v,(as.numeric(df[j,colnum])/WT_lfq[i]))
        #print(v)
      }
    }
  }
  
  return(v)
}
ISPH_peptides <- peptides_Zymo_Eclipse45min_ZM4tag[grep("ZMO0875", peptides_Zymo_Eclipse45min_ZM4tag$Proteins),]
# Peptides to keep track of
peptide <- c("AIEIVDQALDR", "GLPVVDATCPLVNK", "FTDVIGPDTSDICYATQNR")
# Apply ISPH_function to ISPH gene "ZMO0875"
ISPH_lfq <- ISPH_reformat_ZM4("ZMO0875", merged_drb_impute, peptide, ISPH_peptides)
# Apply peptide_FC function to each peptide
ISPH_lfq$AIEIVDQALDR_FC <- peptide_FC(3,ISPH_lfq)
ISPH_lfq$GLPVVDATCPLVNK_FC <- peptide_FC(4,ISPH_lfq)
ISPH_lfq$FTDVIGPDTSDICYATQNR_FC <- peptide_FC(5,ISPH_lfq)
# Fold Change transformed to Log2
ISPH_lfq$AIEIVDQALDR_FC_log2 <- log2(ISPH_lfq$AIEIVDQALDR_FC)
ISPH_lfq$GLPVVDATCPLVNK_FC__log2 <- log2(ISPH_lfq$GLPVVDATCPLVNK_FC)
ISPH_lfq$FTDVIGPDTSDICYATQNR_FC__log2 <- log2(ISPH_lfq$FTDVIGPDTSDICYATQNR_FC)
```

#### **Plot1**  
**ISPH Intensity:**  
Intensity of ISPH protein across strain. Each strain was analyzed in triplicate. 
```{r, echo=FALSE}
type.colors = as.numeric(factor(ISPH_lfq$Type))
q <- ggplot(ISPH_lfq, aes(x=Sample, y=log2(Intensity), fill=Type)) +
  geom_bar(stat = "identity")+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Log2(ISPH protein)", 
                                                                    subtitle = "Across sample types in triplicate",
                                                                    y = "Log2(Intensity)")
```

#### **Plot1 version 2**  
**ISPH Fold Change :**  
Log2 transformed of ISPH protein across strain. Boxplot contains triplicate analysis.
```{r, echo=FALSE}
type.colors = as.numeric(factor(ISPH_lfq$Type))
q <- ggplot(ISPH_lfq, aes(x=Type, y=log2(Intensity), fill=Type)) +
  geom_boxplot()+
  #geom_point(data = ISPH_lfq, aes(x= Type, y= log2(Intensity)), size = 3, color = "#6D696F", alpha = 0.5) +
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Log2(Abundance) ISPH protein", 
                                                                    subtitle = "Across sample types in triplicate",
                                                                    y = "Log2(Intensity)")

#This can only be done if ISPG Rmarkdown has been ran through
ISPG_ISPH_lfq <- rbind(ISPG_lfq[,c(1:2,6,7)], ISPH_lfq[,c(1:2,6,7)])

q <- ggplot(ISPG_ISPH_lfq, aes(x=Type, y=log2(Intensity), fill=Type)) +
  geom_boxplot()+
  #geom_point(data = ISPH_lfq, aes(x= Type, y= log2(Intensity)), size = 3, color = "#6D696F", alpha = 0.5) +
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Log2(Abundance) ISPG and ISOG protein", 
                                                                    subtitle = "Across sample types in triplicate",
                                                                    y = "Log2(Intensity)")



```

#### **Plot2**  
**ISPH Fold Change**  
Fold Change of ISPH protein across strain. Boxplot contains triplicate analysis. 
```{r, echo=FALSE}
type.colors = as.numeric(factor(ISPH_lfq$Type))
q <- ggplot(ISPH_lfq, aes(x=Type, y=FC, fill=Type)) +
  geom_boxplot()+
  #ylim(0,30)+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Fold Change ISPH protein", 
                                                                    subtitle = "Over Expression (OE) Strain",
                                                                    y = "Fold Change (OE/WT)")


Type.colors = as.numeric(factor(ISPG_ISPH_lfq$Type))
q <- ggplot(ISPG_ISPH_lfq[c(1:3,13:14),], aes(x=Type, y=FC, fill=Type)) +
  geom_boxplot()+
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30, by = 5))+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Fold Change ISPG and ISPH protein", 
                                                                    subtitle = "Over Expression (OE) Strain",
                                                                    y = "Fold Change (OE/WT)")

```

#### The following analysis will consider the intensities associated to individual peptides and how the fold changes compare to protein fold changes relative to WT.   
```{r ISPH_peptides, echo=FALSE}
ISPH_peptides_averages <- ISPH_peptides[,c(42,grep("Intensity.IspH", colnames(ISPH_peptides)), grep("Intensity.Isph", colnames(ISPH_peptides)), grep("Intensity.WT", colnames(ISPH_peptides)))]
sub_ISPH_peptides_avg <- ISPH_peptides_averages[,c(1,2,4,5,6,8,9)]
colnames(sub_ISPH_peptides_avg) <- c("PEP","ISPH-1", "ISPH-2", "ISPH-3","WT-1", "WT-2", "WT-3")
rownames(sub_ISPH_peptides_avg) <- ISPH_peptides$Sequence
sub_ISPH_peptides_avg$ISPHAvg <- rowMeans(sub_ISPH_peptides_avg[,grep("ISPH",colnames(sub_ISPH_peptides_avg))])
sub_ISPH_peptides_avg$WTAvg <- rowMeans(sub_ISPH_peptides_avg[,grep("WT",colnames(sub_ISPH_peptides_avg))])
sub_ISPH_peptides_avg$Log2ISPHAvg <- log2(sub_ISPH_peptides_avg$ISPHAvg)
sub_ISPH_peptides_avg$Log2WTAvg <- log2(sub_ISPH_peptides_avg$WTAvg)
sub_ISPH_peptides_avg$ISPHStd <- apply(sub_ISPH_peptides_avg[,grep("ISPH-",colnames(sub_ISPH_peptides_avg))],1,function(x) sd(log2(x)))
sub_ISPH_peptides_avg$WTStd <- apply(sub_ISPH_peptides_avg[,grep("WT-",colnames(sub_ISPH_peptides_avg))],1,function(x) sd(log2(x)))
v <- vector()
#subset peptides with abundance greater than log2
for(i in 1:nrow(sub_ISPH_peptides_avg)){
  if(0 %in% sub_ISPH_peptides_avg[i,2:7])
    v <- append(v,i) 
}
ISPH_peptides_abundance <- sub_ISPH_peptides_avg[-v,]
ISPH_peptides_abundance <- ISPH_peptides_abundance[order(ISPH_peptides_abundance$Log2ISPHAvg),]
ISPH_peptides_abundance$Peptide <- rownames(ISPH_peptides_abundance)
ISPH_peptides_abundance<- ISPH_peptides_abundance %>%
  mutate(Peptide = factor(Peptide, level = rownames(ISPH_peptides_abundance)))
#str(ISPH_peptides_abundance)
#ISPH_peptides_abundance$Peptide
```

```{r peptideRanges_withMeanNotAveraged, echo=FALSE}
t_ISPH_peptides_abundance <-t(ISPH_peptides_abundance[,2:7])
Range_ISPH_peptides <- cbind(ISPH_lfq[c(grep("ISPH",ISPH_lfq$Type),grep("WT", ISPH_lfq$Type)),2],t_ISPH_peptides_abundance)
colnames(Range_ISPH_peptides) <- c("ISPH", colnames(t_ISPH_peptides_abundance))
peptide_FC <- function(df){ 
  
  df_FC <- data.frame(matrix(NA, nrow = nrow(df), ncol = ncol(df)))
  
  for(k in 1:ncol(df)){
    v = numeric(0)
    #print(c("k=",k))
    WT_lfq <- as.numeric(df[grep("WT",rownames(df)),k])
        
    for (j in 1:nrow(df)) {
      #print(c("j=",j))
      for (i in 1:3) {
        #print(c("i=",i))
        if(length(grep(i,rownames(df)[j])) != 0){
          v <- append(v,(as.numeric(df[j,k])/WT_lfq[i]))
          #print(v)
        }
      }
    }
    
   df_FC[,k] <- v
   
  }
  
  colnames(df_FC) <- colnames(df)
  rownames(df_FC) <- rownames(df)
  return(df_FC)
}
Range_ISPH_peptides_FC <- peptide_FC(Range_ISPH_peptides)
Range_ISPH_peptides_FC <- data.frame(matrix(unlist(Range_ISPH_peptides_FC), nrow = length(Range_ISPH_peptides_FC), byrow = T), stringsAsFactors = FALSE)
Range_ISPH_peptides_FC <- Range_ISPH_peptides_FC[,1:3]
rownames(Range_ISPH_peptides_FC) <- colnames(Range_ISPH_peptides)
colnames(Range_ISPH_peptides_FC) <- rownames(Range_ISPH_peptides[1:3,])
Range_ISPH_peptides_FC$AVG_FC <- rowMeans(Range_ISPH_peptides_FC) 
Range_ISPH_peptides_FC$Std_FC <- apply(Range_ISPH_peptides_FC[,1:3],1, FUN = sd)
Range_ISPH_peptides_FC$error <- apply(Range_ISPH_peptides_FC[,1:3],1, function(x) qt(0.975, df=length(x)-1)*sd(x)/sqrt(length(x)))
```

```{r peptide_FC_AveragedWT, echo=FALSE}
peptide_FC_averagedWT <- function(df){
  
  df_FC <- data.frame(matrix(NA, nrow = nrow(df), ncol = ncol(df)))
  
  for(k in 1:ncol(df)){
    v = numeric(0)
    #print(c("k=",k))
    WT_lfq <- mean(as.numeric(df[grep("WT",rownames(df)),k]))
    
        
    for (j in 1:nrow(df)) {
      #print(c("j=",j))
      for (i in 1:3) {
        #print(c("i=",i))
        if(length(grep(i,rownames(df)[j])) != 0){
          v <- append(v,(as.numeric(df[j,k])/WT_lfq))
          #print(v)
        }
      }
    }
    
   df_FC[,k] <- v
  }
  colnames(df_FC) <- colnames(df)
  rownames(df_FC) <- rownames(df)
  return(df_FC)
}
Range_ISPH_peptides_FC_AveragedWT <- peptide_FC_averagedWT(Range_ISPH_peptides)
Range_ISPH_peptides_FC_AveragedWT <- data.frame(matrix(unlist(Range_ISPH_peptides_FC_AveragedWT), nrow = length(Range_ISPH_peptides_FC_AveragedWT), byrow = T), stringsAsFactors = FALSE)
#Range_ISPH_peptides_FC_AveragedWT <- Range_ISPH_peptides_FC_AveragedWT[,1:3]
rownames(Range_ISPH_peptides_FC_AveragedWT) <- colnames(Range_ISPH_peptides)
colnames(Range_ISPH_peptides_FC_AveragedWT) <- rownames(Range_ISPH_peptides)
Range_ISPH_peptides_FC_AveragedWT$AVG_FC <- rowMeans(Range_ISPH_peptides_FC_AveragedWT[,1:3]) 
Range_ISPH_peptides_FC_AveragedWT$AVG_WT_FC <- rowMeans(Range_ISPH_peptides_FC_AveragedWT[,4:6]) 
Range_ISPH_peptides_FC_AveragedWT$Std_FC <- apply(Range_ISPH_peptides_FC_AveragedWT[,1:3],1, FUN = sd)
Range_ISPH_peptides_FC_AveragedWT$Std_WT_FC <- apply(Range_ISPH_peptides_FC_AveragedWT[,4:6],1, FUN = sd)
Range_ISPH_peptides_FC_AveragedWT$error <- apply(Range_ISPH_peptides_FC_AveragedWT[,1:3],1, 
                                                 function(x) qt(0.975, df=length(x)-1)*sd(x)/sqrt(length(x)))
Range_ISPH_peptides_FC_AveragedWT$WT_error <- apply(Range_ISPH_peptides_FC_AveragedWT[,4:6],1, 
                                                    function(x) qt(0.975, df=length(x)-1)*sd(x)/sqrt(length(x)))
Range_ISPH_peptides_FC_AveragedWT <- Range_ISPH_peptides_FC_AveragedWT[c(1,nrow(Range_ISPH_peptides_FC_AveragedWT):2),]
Range_ISPH_peptides_FC_AveragedWT$BioMolecule <- rownames(Range_ISPH_peptides_FC_AveragedWT)
Range_ISPH_peptides_FC_AveragedWT<- Range_ISPH_peptides_FC_AveragedWT %>% 
  mutate(BioMolecule = factor(BioMolecule, level = rev(rownames(Range_ISPH_peptides_FC_AveragedWT))))
```


```{r,echo=FALSE}
ggplot(Range_ISPH_peptides_FC_AveragedWT, aes(x=BioMolecule, y= AVG_FC)) +
  geom_point() +
  geom_point( y = Range_ISPH_peptides_FC_AveragedWT[,1], color = "grey") +
  geom_point( y = Range_ISPH_peptides_FC_AveragedWT[,2], color = "grey") +
  geom_point( y = Range_ISPH_peptides_FC_AveragedWT[,3], color = "grey") +
  geom_errorbar(aes(ymin=AVG_FC-error, ymax=AVG_FC+error) , width = .2, color= "#6D696F", position = position_dodge(0.052)) +
  scale_y_continuous(limits = c(-20,20), breaks = seq(-20,20, by = 5))+
  theme_light()+
  labs(title = "Peptide Fold Changes" ,subtitle = "ISPH and ISPH associated peptides", y = "Fold Change", x ="Peptides") +
  coord_flip() +
  geom_hline(yintercept = 4.709961)+
  geom_hline(yintercept = 6.791636)
  
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r long_format, echo=FALSE}
# reforat ISPH wide format to long
long_ISPH_Lfq <- melt(ISPH_lfq, id.vars = c("Sample"))
variable2 <- long_ISPH_Lfq$variable[long_ISPH_Lfq$variable != "Type"]
long_ISPH_Lfq <- long_ISPH_Lfq[which(long_ISPH_Lfq$variable  %in% variable2),]
long_ISPH_Lfq$value <- as.numeric(long_ISPH_Lfq$value)
long_ISPH_Lfq$variable <- revalue(long_ISPH_Lfq$variable, c("Intensity" = "ISPH","FC" ="ISPH_FC"))
long_ISPH_Lfq$Type <- rep(c("ISPG","ISPH","WT"), times = 11, each=3)
```

#### **Plot 3 version 1**  
**ISPH peptides Ranked Intensities:**  
Dot plot of peptide intensities were averaged (n=3) and then ranked from most abundant to least abundant quantified in the ISPH samples.
```{r, echo=FALSE}
ggplot(ISPH_peptides_abundance, aes(x=Peptide, y= Log2ISPHAvg)) +
  geom_point() +
  theme_light()+
  labs(title = "Average Peptide Abundances" ,subtitle = "ISPH Over Expressed Samples", y = "Log2(Intensity)", x ="Peptides") +
  coord_flip()
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#### **Plot 3 version2**  
**ISPH peptides Ranked Intensities :**  
Bar graph of peptide intensities were averaged (n=3) to produce the bar, error bars are provided for standard deviation. Overlaid are the intensities from each replicate. The peptides are ranked from most abundant to least abundant that were quantified in the ISPH samples.
```{r, echo=FALSE}
ggplot(ISPH_peptides_abundance, aes(x=Peptide, y= Log2ISPHAvg)) + 
  geom_bar(stat = "identity", color = "#6D696F" ,  fill = "#C3DE79", alpha = 0.6, position = position_dodge())+
  geom_errorbar(aes(ymin=Log2ISPHAvg, ymax=Log2ISPHAvg+ISPHStd) , width = .2, color= "#6D696F", position = position_dodge(0.052)) +
  geom_point(data = ISPH_peptides_abundance, aes(x=Peptide, y = log2(ISPH_peptides_abundance$`ISPH-1`)), size = 3, color = "#6D696F", alpha = 0.5) +
  geom_point(data = ISPH_peptides_abundance, aes(x= Peptide, y= log2(ISPH_peptides_abundance$`ISPH-2`)), size = 3, color = "#6D696F", alpha = 0.5) +
  geom_point(data = ISPH_peptides_abundance, aes(x= Peptide, y= log2(ISPH_peptides_abundance$`ISPH-3`)), size = 3, color = "#6D696F", alpha = 0.5) +
  theme_light()+
  labs(title = "Peptide Abundances" ,subtitle = "ISPH Over Expressed Samples", y = "Log2(Intensity)", x ="Peptides") +
  coord_flip()
# theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```


#### **Plot 4**  
**ISPH protein and peptides Log2 transformed Intensities:**  
Box plot of log2 transformed intensities from ISPH protein and associated peptides. There are 3 measurements per boxplot. 
```{r, echo=FALSE}
q <- ggplot(long_ISPH_Lfq[1:36,], aes(x=variable, y=log2(value), fill=Type)) +
  geom_boxplot()+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Intensity across strains", 
                                                                    subtitle = "ISPH and associted peptides in Over Expression (OE) Strain",
                                                                    y = "Log2(Intensity)", x= "")
```

#### **Plot 5**  
**ISPH protein and peptides Log2 transformed fold change: **  
Box plot of fold changes relative to WT for ISPH and the three peptides of interest. This is the most important plot for considering using peptides to monitor over expression at the peptide level versus the protein level.  
```{r, echo=FALSE}
q <- ggplot(long_ISPH_Lfq[37:72,], aes(x=variable, y=log2(value), fill=Type)) +
  geom_boxplot()+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Fold Change across strains", 
                                                                    subtitle = "ISPH and associted peptides in Over Expression (OE) Strain",
                                                                    y = "Log2(Fold Change relative to WT)", x = "")
```

#### **Plot 6**  
**ISPH protein and peptides Log2 transformed fold change: **  
Box plot of fold changes for ISPH and the three peptides of interest and ISPG and it's associated three peptides. This is the most important plot for considering using peptides to monitor over expression at the peptide level versus the protein level. This plot can only be implemented if you have ran the ISG_ISPH_associatedPeptides_plots.Rmd.  
```{r, echo=FALSE}
long_ISPG_Lfq_ONLY <- long_ISPG_Lfq[grep("FC", long_ISPG_Lfq$variable),]
long_ISPG_Lfq_ONLY <- long_ISPG_Lfq_ONLY[-grep("log2",long_ISPG_Lfq_ONLY$variable),]

long_ISPH_Lfq_ONLY <- long_ISPH_Lfq[grep("FC", long_ISPH_Lfq$variable),]
long_ISPH_Lfq_ONLY <- long_ISPH_Lfq_ONLY[-grep("log2", long_ISPH_Lfq_ONLY$variable),]

appended_ISPH_ISPG <- rbind(long_ISPH_Lfq_ONLY, long_ISPG_Lfq_ONLY)
appended_ISPH_ISPG_FC <- appended_ISPH_ISPG[-grep("WT",appended_ISPH_ISPG$Type),]


q <- ggplot(appended_ISPH_ISPG_FC, aes(x=variable, y=log2(value), fill=Type)) +
  geom_boxplot()+
  scale_fill_manual(values = c("#5ABCB2", "#C3DE79","#A394DD"))+
  theme_light()
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Fold Change across strains", 
                                                                    subtitle = "ISPH and associted peptides in Over Expression (OE) Strain",
                                                                    y = "Log2(Fold Change relative to WT)", x = "")
```

```{r, echo = FALSE}
FoldChange_IspH_AIEIVDQDALDR <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/FoldChange_Comparison/IspH_AIEIVDQDALDR_FoldChangeComparison_FAIMS.csv",header = TRUE, sep = ",", stringsAsFactors = FALSE)
FoldChange_IspH_AIEIVDQDALDR$Type <- rep("IspH", 6)
ggplot(FoldChange_IspH_AIEIVDQDALDR, aes(x= Type, y= FoldChange)) + 
  #geom_bar(stat = "identity", color = "#6D696F" ,  fill = "#7C9E3D", alpha = 0.6, position = position_dodge())+
  geom_boxplot()+
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
  ylim(c(0,3.5))+
  theme_light()+
  labs(title = "Transition Fold Changes - FAIMS" ,subtitle = "AIEIVDQDALDR peptide ", y = "Fold Change", x ="Transition")
```

```{r, echo = FALSE}
FoldChange_IspG_ETD <- read.csv("H:/Projects/Proteomics/Zymomona/FAIMS/DataAnalysis/FoldChange_Comparison/IspG_ETDIGVTGGGQGK_FoldChangeComparison_FAIMS.csv",header = TRUE, sep = ",", stringsAsFactors = FALSE)
FoldChange_IspG_ETD$Type <- rep("IspG", 7)
aggplot(FoldChange_IspG_ETD, aes(x= Type, y= FoldChange)) + 
  #geom_bar(stat = "identity", color = "#6D696F" ,  fill = "#7C9E3D", alpha = 0.6, position = position_dodge())+
  geom_boxplot()+
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
  ylim(c(0,4.5))+
  theme_light()+
  labs(title = "Transition Fold Changes - FAIMS" ,subtitle = "ETDIGVTGGGQGK peptide ", y = "Fold Change", x ="Transition")
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
